\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}

\begin{document}

\title{Software Requirements Specification (SRS) Document}
\author{}
\date{\today}

\maketitle

\tableofcontents

\section{Executive Summary}
This Software Requirements Specification (SRS) document outlines the requirements for the development of a comprehensive inventory system. The system aims to provide a secure, scalable, and reliable solution for managing user accounts, roles, and access control. This document serves as a contract between the stakeholders and the development team, ensuring that the system meets the required standards and functionality.

\section{Introduction}
\subsection{Purpose}
The purpose of this SRS document is to provide a detailed description of the requirements for the development of the inventory system.

\subsection{Scope}
The scope of this project includes the development of a web-based inventory system that provides user authentication, role-based access control, and data encryption.

\subsection{Definitions}
\begin{itemize}
\item \textbf{System}: The inventory system to be developed.
\item \textbf{User}: An individual who interacts with the system.
\item \textbf{Administrator}: A user with elevated privileges to manage the system.
\end{itemize}

\subsection{References}
\begin{itemize}
\item Stakeholder Interview Notes
\item Security Best Practices
\item Data Quality Requirements
\end{itemize}

\subsection{Overview}
The system will be built using a web-based architecture and hosted on a cloud-based infrastructure. The system will provide a user interface to manage user accounts and roles, as well as a mechanism for users to reset their passwords.

\section{Overall Description}
\subsection{Product Perspective}
The system will be a web-based application that interacts with a centralized identity management system.

\subsection{Product Functions}
The system will provide the following functions:
\begin{itemize}
\item User authentication
\item Role-based access control
\item Data encryption
\item Error handling and logging
\item Data backup and disaster recovery
\end{itemize}

\subsection{User Characteristics}
The users of the system will be administrators and end-users. Administrators will have elevated privileges to manage the system, while end-users will have limited access.

\subsection{Constraints}
The system will be built using a web-based architecture and hosted on a cloud-based infrastructure.

\subsection{Assumptions}
\begin{itemize}
\item The system will be built using a web-based architecture.
\item The system will be hosted on a cloud-based infrastructure.
\end{itemize}

\section{Specific Requirements}

\subsection{Functional Requirements}

\subsubsection{REQ-001: User Authentication}
The system shall authenticate user credentials against a centralized identity management system.

\begin{itemize}
\item \textbf{Description}: The system will verify user credentials against a centralized identity management system.
\item \textbf{Inputs}: User credentials (username and password)
\item \textbf{Outputs}: Authentication result (success or failure)
\item \textbf{Processing Logic}: The system will use a secure authentication protocol to verify user credentials.
\item \textbf{Business Rules}: The system will enforce a password policy that requires passwords to be changed every 90 days.
\item \textbf{Exception Handling}: The system will display an error message if authentication fails.
\item \textbf{Acceptance Criteria}: The system shall authenticate user credentials successfully.
\end{itemize}

\subsubsection{REQ-002: Single Sign-On (SSO)}
The system shall provide a single sign-on (SSO) capability for all authorized users.

\begin{itemize}
\item \textbf{Description}: The system will provide a single sign-on capability for all authorized users.
\item \textbf{Inputs}: User credentials (username and password)
\item \textbf{Outputs}: SSO token
\item \textbf{Processing Logic}: The system will use a secure authentication protocol to generate an SSO token.
\item \textbf{Business Rules}: The system will enforce a session timeout policy.
\item \textbf{Exception Handling}: The system will display an error message if SSO fails.
\item \textbf{Acceptance Criteria}: The system shall provide a single sign-on capability successfully.
\end{itemize}

\subsubsection{REQ-003: Input Data Validation}
The system shall validate user input data to prevent SQL injection attacks.

\begin{itemize}
\item \textbf{Description}: The system will validate user input data to prevent SQL injection attacks.
\item \textbf{Inputs}: User input data
\item \textbf{Outputs}: Validation result (success or failure)
\item \textbf{Processing Logic}: The system will use a secure validation protocol to verify user input data.
\item \textbf{Business Rules}: The system will enforce data validation rules.
\item \textbf{Exception Handling}: The system will display an error message if validation fails.
\item \textbf{Acceptance Criteria}: The system shall validate user input data successfully.
\end{itemize}

\subsection{Non-Functional Requirements}

\subsubsection{NFR-001: Performance}
The system shall respond to user requests within 2 seconds.

\begin{itemize}
\item \textbf{Description}: The system will respond to user requests within 2 seconds.
\item \textbf{Measurable Criteria}: The system shall respond to user requests within 2 seconds.
\end{itemize}

\subsubsection{NFR-002: Security}
The system shall ensure that all data transmitted between the client and server is encrypted using TLS 1.2 or later.

\begin{itemize}
\item \textbf{Description}: The system will ensure that all data transmitted between the client and server is encrypted using TLS 1.2 or later.
\item \textbf{Measurable Criteria}: The system shall ensure that all data transmitted between the client and server is encrypted using TLS 1.2 or later.
\end{itemize}

\subsection{Interface Requirements}

\subsubsection{REQ-INT-001: User Interface}
The system shall provide a user interface to manage user accounts and roles.

\begin{itemize}
\item \textbf{Description}: The system will provide a user interface to manage user accounts and roles.
\item \textbf{Inputs}: User input (username, password, role)
\item \textbf{Outputs}: User account and role information
\item \textbf{Processing Logic}: The system will use a secure authentication protocol to manage user accounts and roles.
\item \textbf{Business Rules}: The system will enforce a role-based access control policy.
\item \textbf{Exception Handling}: The system will display an error message if user account or role management fails.
\item \textbf{Acceptance Criteria}: The system shall provide a user interface to manage user accounts and roles successfully.
\end{itemize}

\section{Appendices}

\subsection{Data Dictionary}
\begin{itemize}
\item \textbf{User}: An individual who interacts with the system.
\item \textbf{Administrator}: A user with elevated privileges to manage the system.
\item \textbf{Role}: A set of privileges assigned to a user.
\end{itemize}

\subsection{Traceability Matrix}
\begin{longtable}{|l|l|}
\hline
REQ-ID & Source/Justification \\
\hline
REQ-001 & Stakeholder Interview Notes, Section 3.1 \\
REQ-002 & Stakeholder Interview Notes, Section 3.2 \\
REQ-003 & Security Best Practices \\
... & ... \\
\hline
\end{longtable}

\subsection{Risk Analysis}
The following risks have been identified:
\begin{itemize}
\item \textbf{Risk 1}: The system may not meet performance requirements.
\item \textbf{Risk 2}: The system may not ensure data security.
\end{itemize}

\subsection{Assumptions and Constraints}
\begin{itemize}
\item \textbf{Assumptions}:
+ The system will be built using a web-based architecture.
+ The system will be hosted on a cloud-based infrastructure.
\item \textbf{Constraints}:
+ The system shall be developed within 6 months.
+ The system shall be deployed on a cloud-based infrastructure.
\end{itemize}

\section{Approval Signature Blocks}
This SRS document has been approved by the following stakeholders:

\begin{itemize}
\item \textbf{Project Manager}: [Name]
\item \textbf{Business Analyst}: [Name]
\item \textbf{Technical Lead}: [Name]
\end{itemize}

\section{Version Control Information}
This SRS document is version 1.0 and was last updated on \today.

\end{document}